\mireval{}:\\ A Transparent Implementation of Common MIR Metrics

### 2014-10-12 paper/poster.tex
Final poster

\begin{posterbox}[column=0]{Abstract}
We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
We performed a quantitative comparison of \mireval{} to existing evaluation systems to explore differences in implementation.
\end{posterbox}

\begin{posterbox}[column=0,below=auto]{Design}

@@

\begin{posterbox}[column=1]{Comparison to Existing Implementations}

@@

\begin{posterbox}[column=0,below=auto,span=2]{Average Relative Difference of \mireval{} vs. MIREX}

@@

\begin{posterbox}[column=0,below=auto,span=2,boxColorOne=white]{}

\begin{minted}[bgcolor=mintedbg, frame=single, framerule=0pt, fontsize=\large]{python}
import mir_eval
# Load in beat annotations
reference_beats = mir_eval.io.load_events('reference_beats.txt')
estimated_beats = mir_eval.io.load_events('estimated_beats.txt')
# scores will be a dictionary where the key is the metric name and the value is the score achieved
scores = mir_eval.beat.evaluate(reference_beats, estimated_beats)
# evaluate() will pass keyword args to the metric functions
scores = mir_eval.beat.evaluate(reference_beats, estimated_beats, f_measure_threshold=0.05)
# You can also perform pre-processing and compute each metric manually
reference_beats = mir_eval.beat.trim_beats(reference_beats)
estimated_beats = mir_eval.beat.trim_beats(estimated_beats)
f_score = mir_eval.beat.f_measure(reference_beats, estimated_beats, f_measure_threshold=0.05)
\end{minted}

$\;$\\[-1em]

\begin{minted}[bgcolor=mintedbg, frame=single, framerule=0pt, fontsize=\large]{c}
> ./onset_eval.py reference_onsets.txt estimated_onsets.txt -o output.json
reference_onsets.txt vs. estimated_onsets.txt
  F-measure : 0.531
  Precision : 0.481
     Recall : 0.591
Saving results to:  output.json
\end{minted}

>>>>

\begin{posterbox}[name=abstract,column=0]{Abstract}
We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.
We performed a quantitative comparison of \mireval{} to existing evaluation systems to explore differences in implementation.
\end{posterbox}

\begin{posterbox}[name=design,column=0,below=abstract]{Design}

@@

\begin{posterbox}[name=comparison,column=1]{Comparison to Existing Implementations}

@@

\begin{posterbox}[name=average,column=0,below=design,span=2]{Average Relative Difference of \mireval{} vs. MIREX}

@@

\begin{posterbox}[name=python,column=0,below=average]{Using \mireval{} in Python}

\begin{minted}[bgcolor=boxcolor, frame=single, framerule=0pt]{python}
import mir_eval
# Load in beat annotations
reference_beats = mir_eval.io.load_events('ref_beats.txt')
estimated_beats = mir_eval.io.load_events('est_beats.txt')
# scores will be a dictionary where the key is the metric name
# and the value is the score achieved
scores = mir_eval.beat.evaluate(reference_beats, estimated_beats)
# evaluate() will pass keyword args to the metric functions
scores = mir_eval.beat.evaluate(reference_beats, estimated_beats,
                                f_measure_threshold=0.05,
                                cemgil_sigma=0.02)
# You can also perform pre-processing and compute metrics manually
reference_beats = mir_eval.beat.trim_beats(reference_beats)
estimated_beats = mir_eval.beat.trim_beats(estimated_beats)
f_meas = mir_eval.beat.f_measure(reference_beats, estimated_beats,
                                 f_measure_threshold=0.05)
cemgil = mir_eval.beat.cemgil(reference_beats, estimated_beats,
                              cemgil_sigma=0.02)
\end{minted}

\begin{posterbox}[name=evaluator,column=1,below=average]{Using the evaluator scripts}

\begin{minted}[bgcolor=boxcolor, frame=single, framerule=0pt]{bash}
> ./onset_eval.py ref_beats.txt est_beats.txt -o scores.json

  ref_beats.txt vs. est_beats.txt
                          F-measure : 0.622
                             Cemgil : 0.362676699474
           Cemgil Best Metric Level : 0.362676699474
                               Goto : 0.000
                            P-score : 0.828185328185
    Correct Metric Level Continuous : 0.0328185328185
         Correct Metric Level Total : 0.65444015444
        Any Metric Level Continuous : 0.0328185328185
             Any Metric Level Total : 0.65444015444
                   Information gain : 0.20492902479
  Saving results to:  scores.json

> cat scores.json

  {"F-measure": 0.6216216216216, "Cemgil": 0.36267669947376, ...
\end{minted}

\begin{posterbox}[name=url,column=0,below=python,span=2,boxColorOne=white]{}
